A Meta-Analysis of Music Emotion Recognition Studies

### 2025-04-11 index.qmd
web site improvements and folder clean

# README

@@

## Plan

@@

### Study Search and Selection

@@

### Data Extraction and Coding

@@

### Analysis

Data analysis is covered in [analysis/analysis.qmd](analysis/analysis.qmd) document.

### Manuscript

The study report is available [manuscript/manuscript.qmd](manuscript/manuscript.qmd) document.

### Common datasets

Commonly used datasets [manuscript/datasets.qmd](manuscript/datasets.qmd).

>>>>

---
title: "A Meta-Analysis of Music Emotion Recognition Studies"
author:
  - name: Tuomas Eerola
    orcid: 0000-0002-2896-929X
    email: tuomas.eerola@durham.ac.uk
    affiliations:
      - name: Durham University
  - name: Cameron J. Anderson
    orcid: 0000-0002-8737-2055
    email: andersoc@mcmaster.ca
    affiliations:
      - name: McMaster University
description: "A Meta-Analysis of Music Emotion Recognition Studies."
date: 4-11-2025
title-block-style: default
---

@@

### Plan

@@

#### Study Search and Selection

@@

#### Data Extraction and Coding

@@

#### Analysis

Data analysis steps are covered in the [analysis/analysis.qmd](analysis/analysis.qmd) document.

#### Manuscript

The study report is available in [manuscript/manuscript.qmd](manuscript/manuscript.qmd) document.

#### Common datasets

Commonly used datasets are available in [manuscript/datasets.qmd](manuscript/datasets.qmd).

### 2025-04-11 manuscript/_figure3.qmd
web site improvements and folder clean

#gridExtra::grid.arrange(fp1, fp2, ncol=2, widths=c(2,1))
#ggarrange(fp1,fp2, ncol = 2, labels = c("A","B"),widths=c(2,1)) # added labels A and B
ggarrange(fp1) #  
ggsave(filename = 'figure3.pdf', width = 12, height = 6, units = 'in',fp1)

>>>>

#gridExtra::grid.arrange(fp1, fp2, ncol=2, widths=c(2,1))
#ggarrange(fp1,fp2, ncol = 2, labels = c("A","B"),widths=c(2,1)) # added labels A and B
ggarrange(fp1) #  
#ggsave(filename = 'figure3.pdf', width = 12, height = 6, units = 'in',fp1)

### 2025-04-11 manuscript/_figure4.qmd
web site improvements and folder clean

#gridExtra::grid.arrange(fp1, fp2, ncol=2, widths=c(2,1))
#ggarrange(fp1,fp2, ncol = 2, labels = c("A","B"),widths=c(2,1)) # added labels A and B
ggarrange(fp1)
ggsave(filename = 'figure4.pdf', width = 12, height = 6, units = 'in',fp1)

>>>>

#gridExtra::grid.arrange(fp1, fp2, ncol=2, widths=c(2,1))
#ggarrange(fp1,fp2, ncol = 2, labels = c("A","B"),widths=c(2,1)) # added labels A and B
ggarrange(fp1)
#ggsave(filename = 'figure4.pdf', width = 12, height = 6, units = 'in',fp1)
